---
title: "Music and Mental Health"
subtitle: "How does music genres and mental health connect?"
author: "Ivy Spratt"
execute:
  echo: FALSE
  message: FALSE
  warning: FALSE
---

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(primer.data)
library(gtsummary)
library(brms)
library(tidybayes)
library(gt)
library(tidyr)
library(ggplot2)
library(dplyr)
```

```{r}
#| message: false

df <- read_csv("data/mxmh_survey_results.csv")
```

```{r}
df_filtered <- df |> 
  rename(music_effects = "Music effects",
         fav_genre = "Fav genre",
         depression = "Depression",
         anxiety = "Anxiety",
         insomnia = "Insomnia",
         ocd = "OCD") |> 
  select(fav_genre, depression, anxiety, insomnia, ocd, music_effects) |> 
  filter(!is.na(fav_genre), 
         !is.na(depression), 
         !is.na(music_effects), 
         !is.na(anxiety), 
         !is.na(insomnia), 
         !is.na(ocd))
```

```{r}
df_filtered$depression <- as.numeric(df_filtered$depression)

df_filtered$anxiety <- as.numeric(df_filtered$anxiety)

df_filtered$insomnia <- as.numeric(df_filtered$insomnia)

df_filtered$ocd <- as.numeric(df_filtered$ocd)
```

Music has a big effect on how we live our lives, especially our mental health. In a study that collected data from a Google form, we seek to evaluate if there is a relationship between genres of music and whether or not their listeners have high or low levels of depression. The goal is to better understand the correlation between music genres and depression, and possibly evaluate any trends between the two. We modeled depression, and it's scale on 1-10 (1 being the respondent doesn't experience it, 10 being the respondent experiences it often), as a logistic function of Gospel music and music effects. Gospel music seems to have little effect, however still decreases depression levels. The genre that is most associated with low depression rates and has the most likelihood to improve depression levels is Gospel music, reporting that people who listen to it often have 1.0 level of depression lower than others. 

```{r}
colors <- c("#B0D9E8", "#A6C0D7", "#6D8EAE", "#2D4F6D", "#1C2D40", 
            "#004B6A", "#003B5C", "#003248", "#002B40", "#001F2D", 
            "#004C6C", "#003C5C", "#00324D", "#00242D", "#001F3F", 
            "#001A33")

ggplot(df_filtered, aes(x = fav_genre, 
                        y = depression,
                        fill = fav_genre)) +
  geom_bar(stat = "summary", 
           fun = "mean", 
           position = position_dodge(0.9), 
           width = 0.7) +
  scale_fill_manual(values = colors) +
  labs(x = "",
       y = "Average Depression Level",
       title = "Depression Scores by Favorite Music Genre and Music Effects") +
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1),
                                   legend.position = "none")
```

