---
title: "Model"
subtitle: "Which genre's listeners have the lowest depression levels?"
execute:
  echo: FALSE
  message: FALSE
  warning: FALSE
---

```{r}
#| label: setup
#| message: false
#| warning: false
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)

df <- read_csv("data/mxmh_survey_results.csv")
```

```{r}
df_filtered <- df |> 
  rename(music_effects = "Music effects",
         fav_genre = "Fav genre",
         depression = "Depression",
         anxiety = "Anxiety",
         insomnia = "Insomnia",
         ocd = "OCD",
         lofi_freq = "Frequency [Lofi]",
         gospel_freq = "Frequency [Gospel]") |> 
  select(fav_genre, depression, anxiety, insomnia, ocd, music_effects, gospel_freq, lofi_freq) |> 
  filter(!is.na(fav_genre), 
         !is.na(depression), 
         !is.na(music_effects), 
         !is.na(anxiety), 
         !is.na(insomnia), 
         !is.na(ocd))
```

To answer the question of which genre is the best to listen to, we first have to see which of the favorite genres are most associated with high/low levels of depression, by using a bayesian regression model. For this initial model, we are using this formula:

$$
depression_{i} = \beta_{0} + \beta_{1} fav\_genre_i
$$
```{r}
#| label: general analysis
#| cache: true

fit_gen <- brm(formula = depression ~ fav_genre,
                  data = df_filtered,
                  family = gaussian(),
                  refresh = 0,
                  silent = 2,
                  seed = 9)

tbl_regression(fit_gen)
```

We see that on average, gospel listeners generally have lower levels of depression, while lofi listeners generally have higher levels of depression. 

Like every bayesian regression model, this model is not completely accurate in that it was only sent out on a couple social media platforms (Reddit, Discord, other social media), which doesn't include data from people not involved online, and was advertised on posters and business cards (which restrict the data to a certain proximity).

```{r}
#| label: gospel and lofi analysis
#| cache: true

fit_gospel <- brm(formula = depression ~ gospel_freq,
                  data = df_filtered,
                  family = gaussian(),
                  refresh = 0,
                  silent = 2,
                  seed = 9)
```


To give us a baseline of how listening to gospel music impacts your depression levels, we evalute it alone so we can evaluate how much lower gospel listeners' depression levels are. We do that by taking the frequency of how often people listen to Gospel music. 

```{r}
#| cache: true

tbl_regression(fit_gospel)
```

In summary, there is no definite genre that listening to increases or decreases depression levels, though listening to the gospel genre might make a bit of an effect. Although, since Gospel listeners on average might have lower depression levels, the only conclusion we can make is that Gospel listeners, on average, have the lowest levels of depression.




